RCloud: Integrating Exploratory Visualization, Analysis and Deployment

### 2014-03-25 introduction.tex
merge

\todo{Points we want to make."Coordination is done by meetings" "how do you trace an automated alert back to an EDA environment ?"}

@@

\begin{itemize}
\item Technology transfer. Experiments in notebooks developed by analysts need to become accessible in the production environment, making it easy to push new features, prototypes, etc.
\item Dashboarding. To support the above, there should be a mode in which non-experts
can operate the experiments without coding.
\item Version control as a primary concept in the repository. There needs to be a way to control the visibility of prototypes as they are being developed and tested.
\item Modern interactive technologies. People want to interact with data to explore it. Scalable technologies like crossfilter exist. Want to support those in the context of an R environment. Need to support full 2-way communication between computing in the cloud and interaction on the web.
\item Other requirements e.g. Kandel's user study. Not our contribution but things we must address, mentioned in related work section. Heer/Agrawala design considerations for collaborative visual analytics.
\end{itemize}

% What is the scope of our solution?
Our investigation focuses on the R language \cite{RCoreTeam:2013:R}
for statistical computing and graphics. R is one of the most popular
systems for data analysis and is well-supported by 
a complex ecosystem of compatible packages, software
tools and other resources. Of importance to us, there are
packages for high performance computing in the cloud,
and for generating web graphics.

>>>>

%% \todo{Points we want to make."Coordination is done by meetings" "how do you trace an automated alert back to an EDA environment ?"}

@@

\begin{itemize}
\item Constant technology transfer. Experiments in notebooks developed
by analysts need to become accessible in the production environment,
making it easy to push new features, prototypes, etc.
\item Dashboarding. To support the above, there should be a mode in which non-experts
can operate the experiments without coding.
\item Version control as a primary concept in the repository. There
needs to be a way to control the visibility of prototypes as they are
being developed and tested.
\item Coexistence in the current data ecosystem. We perceive the
isolation of current exploratory visualization and data analysis
environments to be a serious threat to a wider adoption of modern
techniques.
\item Modern interactive technologies. current isolation
notwithstanding, we find there is business demand for interactive
visualization tools. The main challenge here is how to integrate
these technologies so data scientists and statisticians can target
them, \emph{and} business-facing users can use them.
%% Scalable technologies like crossfilter exist. Want to support those in the context of an R environment. Need to support full 2-way communication between computing in the cloud and interaction on the web.
%% \item Other requirements e.g. Kandel's user study. Not our contribution but things we must address, mentioned in related work section. Heer/Agrawala design considerations for collaborative visual analytics.
\end{itemize}

% What is the scope of our solution?
Our investigation focuses on the R language \cite{RCoreTeam:2013:R}
for statistical computing and graphics. R is one of the most popular
systems for data analysis and is well-supported by
a complex ecosystem of compatible packages, software
tools and other resources.
%
Of importance to us, there are existing
packages for high performance computing in the cloud,
and for generating web graphics. % no, there aren't. we wrote those!
